Figures

### 2019-05-13 figures/07_model-selection.Rmd
Setup model summary infrastructure

>>>>

# evaulate fixed effects
# ag + {maxdepth, baseflow, iwslavratio}

(model_forms <- list(
  "ag" = bf(tp ~ ag), 
  "depth+bf" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean),
  "depth+iwsla" = bf(tp ~ ag + maxdepth + iwslavratio), 
  "all" = bf(tp ~ ag + maxdepth + hu12vbaseflowvmean + iwslavratio) 
))

fe_brms <- 
  lapply(seq_along(model_forms), function(i) 
    get_if_not_exists(brm_fit, 
                      paste0("../data/mcmc/fe/", names(model_forms)[i]), 
                      formula = model_forms[[i]], 
                      data = dt))

dplyr::bind_rows(
  lapply(fe_brms, function(x) data.frame(brms::bayes_R2(x)))) %>%
  mutate(Model = names(model_forms), 
         Response = "TP", 
         Estimate = round(Estimate, 2)) %>%
  dplyr::select(Response, Model, Estimate)

# evaulate spatial random effects
# {fixed effects} + 1/ag, 1/soybeans, 1/corn
